---
title: "Documentation for the custom functions of the ocr project"
author: Calixte HENRY
output: 
  html_document:
    theme: default # light theme
    #theme: darkly # dark theme 
    toc: yes
---

# image_processing_function_even.R

```{r eval=FALSE, message=FALSE, warning=FALSE, highlight=TRUE, paged.print=FALSE}
process_image_even <- function(image) {
  info <- image_info(image)
  
  # Image processing operations
  im_p <- image %>%
    image_convert(colorspace = "gray") %>% 
    image_scale(geometry = "2000x") %>% 
    image_threshold("white", threshold = "85%") %>%
    image_threshold("black", threshold = "80%") %>%
    image_median(radius = 4) %>%
    image_blur(radius = 2, sigma = 1.5) %>%
    image_enhance()
}
```

Details of each line:

1\. turn the image to gray scale

2\. Scale the image to 2000x (2000 width), we keep aspect ratio (by not telling the height)

3\. Threshold white 85%: all pixels more than 15% white are turn to full white pixels.

4\. same for black, 20% of black are turned to full black pixels.

5\. image_median is a smoothing function, the algorithm replaces each pixel with the median color in a circular neighborhood. It "rounds" the letters a bit.

6\. Blur is used for th esame purposed, it limits the sharp edges of the tiny letters, making them easier to read by ocr.

7\. image_enhance is supposed to minimize noise (random odd color pixels)

# image_processing_function_odd.R

```{r, eval=FALSE, highlight=TRUE}
process_image_odd <- function(image) {
  info <- image_info(image)
  
  # Image processing operations
  im_p <- image %>%
    image_convert(colorspace = "gray") %>% 
    image_scale(geometry = "2000x") %>% 
    image_threshold("white", threshold = "75%") %>%
    image_threshold("black", threshold = "40%") %>%
    image_median(radius = 4) %>%
    image_blur(radius = 2, sigma = 1.5) %>%
    image_enhance()
}
```

Details of each line:

1\. turn the image to gray scale

2\. Scale the image to 2000x (2000 width), we keep aspect ratio (by not telling the height)

3\. Threshold white 75%: all pixels more than 25% white are turn to full white pixels.

4\. same for black, 20% of black are turned to full black pixels.

5\. image_median is a smoothing function, the algorithm replaces each pixel with the median color in a circular neighborhood. It "rounds" the letters a bit.

6\. Blur is used for the same purposed, it limits the sharp edges of the tiny letters, making them easier to read by OCR.

7\. image_enhance is supposed to minimize noise (random odd color pixels)

# split_and_process_ocr_text.R

```{r, eval=FALSE, highlight=TRUE}
split_and_process_ocr_text <- function(text) {
  processed_dataset <- tibble(text = unlist(strsplit(text, "\n"))) %>%
    mutate(content = str_replace(text, "\\.\\s+\\.", "..")) %>%
    mutate(content = str_replace(content, "\\.\\,\\.", "..")) %>%
    mutate(content = str_replace(content, "^(\\p{L})\\s", "")) %>% 
    mutate(content = str_replace_all(content, "\\[|\\]|\\}|\\{|\\!|(,<=\\.\\))", "|")) %>%
    mutate(content = str_replace(content, "^\\s*\\|+\\s*", "")) %>% 
    mutate(content = str_replace(content, "(?<=\\.\\.)1", "|")) %>% 
    mutate(content = str_replace_all(content, "(\\.{2,})\\s*([A-Za-z0-9])", "\\1|\\2")) %>%
    mutate(content = str_trim(content, side = "left")) %>% 
    mutate(content = str_replace(content, "(.)(dem)", "i\\2")) %>% 
    mutate(content = str_replace(content, "^\\d+\\s*", "|'")) %>% 
    mutate(content = str_replace_all(content, "([^a-zA-Z])(La|Le|L')([^a-zA-Z])", function(x) {
      if (is.na(x) || str_detect(x, "\\([a-zA-Z]+\\)")) {
        return(x)
      } else {
        return(paste0(str_extract(x, "([^a-zA-Z])"), "(", str_extract(x, "(La|Le|L')"), ")", str_extract(x, "([^a-zA-Z])")))
      }
    })) %>%
    mutate(content = str_replace_all(content, "\\s*(\\d{1,3}[.,]\\d{1,3}[^\\|]*)", function(x) {
      return(paste0("|", x, "|"))
    })) %>%
    mutate(content = 
             {
               if (any(str_detect(content, "(\\d{1,3}[.,]{1}\\d{1,3})"))) {
                 str_replace_all(content, "\\s*(\\d{1,3}[.,]\\d{1,3})", "\\|\\0\\|")
               } else {
                 str_replace_all(content, "\\d{1,3}\\s+", "\\|\\0\\|")
               }
             }) %>% 
    mutate(content = str_replace_all(content, "\\|\\s*\\|*", "|")) %>% 
    mutate(arg = str_split(content, "(?<!\\d)\\.+(?!\\d)")) %>% 
    mutate(arg = as.character(arg)) %>% 
    mutate(arg = str_replace_all(arg, "\", \"", "")) %>%
    mutate(arg = str_replace_all(arg, "^c\\(\"|\"\\)$", "")) %>% 
    separate_wider_delim(arg, delim = "|", names_sep = "", too_few = "align_start")
  
  return(processed_dataset)
}
```

----------------------- Breakdown of the function ---------------------------

```{r, eval=FALSE, highlight=TRUE}

processed_dataset \<- tibble(text = unlist(strsplit(text, "\n"))) %\>%
```

split the text by new lines "\n", then turn the list of these texts to a dataset. Getting ready for all the text cleanning.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(value, "\\.\\s+\\.", "..")) %\>% 
  mutate(content = str_replace(content, "\\.\\,\\.", "..")) %\>% 
```

remove whitespaces (comma for the second line) in between sequences of periods ".. ... -\> ....."

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(content, "\^(\\p{L})\\s", "")) %\>%
```

Remove alone leading letter followed by whitespace at beg of strings.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace_all(content, "\\[\|\\]\|\\}\|\\{\|\\!\|(,\<=\\.\\))", "\|")) %\>% 
```

replace all occurrences of square brackets, curly braces, exclamation marks, and the pattern (,\<=.)) with a vertical bar (\|).

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(content, "\^\\s*\\\|+\\s*", "")) %\>%
```

removes any leading whitespace and vertical bars from the content strings.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(content, "(?\<=\\.\\.)1", "\|")) %\>%
```

replaces any occurrences of "..1" with a vertical bar (\|).

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace_all(content, "(\\.{2,})\\s\*([A-Za-z0-9])", "\\1\|\\2")) %\>% 
```

replace any sequence of two or more periods followed by optional whitespace and then a letter or digit with the sequence of periods, a vertical bar, and the letter or digit.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_trim(content, side = "left")) %\>%
```

removes any leading whitespace from the content strings.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(content, "(.)(dem)", "i\\2")) %\>% 
```

replaces any occurrence of a single character followed by "dem" with "idem".

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace(content, "\^\\d+\\s\*", "\|'"))
```

replaces any leading digits followed by optional whitespace with a vertical bar and a single quote (\|')

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace_all(content, "([\^a-zA-Z])(La\|Le\|L')([\^a-zA-Z])", function(x) { if (is.na(x) \|\| str_detect(x, "\\([a-zA-Z]+\\)")) { return(x) } else { return(paste0(str_extract(x, "([\^a-zA-Z])"), "(", str_extract(x, "(La\|Le\|L')"), ")", str_extract(x, "([\^a-zA-Z])"))) } })) 
```

replaces any occurrences of [any alpha symbol]("La" or "Le" or "L'")[any alpha symbol] by itself if the string is == NA or has parenthesis around a word by a reconstructed matched text by extracting the non-alphabetic characters before and after the "La", "Le", or "L'" and inserting the "La", "Le", or "L'" between them.

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace_all(content, "\\s*(\\d{1,3}[.,]\\d{1,3}[\^\\\\\|]*)", function(x) { return(paste0("\|", x, "\|")) })) %\>%
```

find any sequence of 1 to 3 digits, followed by a period or comma, followed by 1 to 3 more digits, and optionally followed by any non-vertical bar characters. replaces it by the match wrapped in "\|" : \|match\|

```{r, eval=FALSE, highlight=TRUE}
mutate(contents = { if (any(str_detect(content, "(\\d{1,3}[.,]{1}\\d{1,3})"))) { str_replace_all(content, "\\s\*(\\d{1,3}[.,]\\d{1,3})", "\\\|\\0\\\|") } else { str_replace_all(content, "\\d{1,3}\\s+", "\\\|\\0\\\|") } })
```

This code find digits and enclose them into pipes. We use a "if" statement because we differentiate 2 cases: when the number has decimals and when it doesn't. "if" statement correspond to number with digits (123,456) "else" statement are the other numbers the match is returned enclosed into pipes \|123,456\|

```{r, eval=FALSE, highlight=TRUE}
mutate(content = str_replace_all(content, "\\\|\\s*\\\|*", "\|")) %\>%
```

replace any sequence of pipes (including pipes with whitespaces inbetween) by a single pipe "\|\| \|\|\|" --\> "\|"

```{r, eval=FALSE, highlight=TRUE}
mutate(arg = str_split(content, "(?\<!\\d)\\.+(?!\\d)")) %\>%
```

is used to keep the relevant content of each string. split the string based on a pattern that catch sequence of 1 or more dots. output is a vector containing all that was in between the sequences of dots.

"Bert....................\| Houille..............\| 1,337 62.125 361\|" --\> "Bert" "\| Houille" "\| 1,337 62.125 361\|"

```{r, eval=FALSE, highlight=TRUE}
mutate(arg = as.character(arg)) %\>%
```

turn to character class

```{r, eval=FALSE, highlight=TRUE}
mutate(arg = str_replace_all(arg, "", "", "")) %\>% mutate(arg = str_replace_all(arg, "\^c\\("\|"\\)\$", "")) %\>%
```

These lines are used to remove the c(" "), that appears after converting to char class first line remove the " second line removes the "c(" and the ")"

```{r, eval=FALSE, highlight=TRUE}
separate_wider_delim(arg, delim = "\|", names_sep = "", too_few = "align_start")
```

cut the arg var into pieces based on the delimiter "\|". We obtain the final form of the dataset with the "arg" split for each distinct element of the string.
